\documentclass[margin]{res} 
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{lmodern}

\begin{document}


\begin{center}

\begin{large}
\textbf{Michael E. Rhodes}\\
\end{large}

Chicago, IL 60640 • (847) 909-6486\\
www.rhostats.com • mrhodes262@gmail.com \\[3pt]

\end{center}


\begin{resume}

\section{Objective} Experienced data scientist with over four years of experience looking to leverage knowledge of programming and databases in a software development position.

\section{Experience}
 {\bf Information Resources, Inc} - Chicago, IL \hfill June 2012 - Present\\
 \textit{Analyst II}\\
 {Responsible for the creation and delivery of new analytics products to retail and manufacturer clients.}
 
 \begin{itemize} \itemsep -2pt  % reduce space between items
	\item Consulted many assortment analytics projects for Walmart and other retailers (including data pull, analysis in R or Python and delivery of insights).
	\item Automated time consuming data pulls and reporting using Python.
 	\item Contributed to the creation of a store grouping algorithm, which was implemented in R.
 \end{itemize}
 
 {\bf RocketClicks} - Milwaukee, WI \hfill January 2012 - June 2012\\
 \textit{Pay-Per-Click Analyst}
 \begin{itemize} \itemsep -2pt
  	\item Gained significant experience managing large online advertising campaigns, as well as
writing Excel macros.
 	\item Automated and standardized analysis of online advertising performance across various
platforms for one of Rocket Clicks' largest clients.
 \end{itemize}
 
\section{Education} 
\textbf{Marquette University} - Milwaukee, WI \hfill January 2009 - December 2011 \\
\textit{B.S. in Applied Mathematical Economics}

\begin{itemize} \itemsep -2pt  % reduce space between items
	\item Program emphasized leveraging computer modeling and statistical analysis of real-world economic problems.
 	\item Coursework included use of SAS, MATLAB and EViews for completion of econometrics/regression analysis, statistics and mathematical modeling courses (among others).
\end{itemize}

\textbf{Holy Cross College} - Notre Dame, IN \hfill August 2007 - December 2008 \\
\textit{Economics}

\section{Technical Skills}
    {\bf Languages} - Python, R, and JavaScript\\
	{\bf Databases} - Oracle/Microsoft SQL, MongoDB, and CouchDB\\
	{\bf Web Development} - Node.js, Express.js, Bootstrap.css, JQuery, Ajax, and Django\\
	{\bf Operating Systems} - Linux (Ubuntu), OS X, and Windows\\
    {\bf Software} - Tableau, Alteryx, and Excel (VBA)\\
    {\bf Other} - Git, {\LaTeX}, and Shell Scripting (Unix)

\section{Additional Projects} \hfill \textit{See additional projects here: https://github.com/mike-rhodes}\\
	{\bf RhoStats.com} - Personal blog build using the MEAN stack and hosted on Heroku. Will feature current and future side projects.\\
	{\bf Twitter Analysis} - Twitter tone analysis using machine learning alogrithms. Implemented in Python and stored in MongoDB.

\section{Achievements}
    {\bf IRI CEO Award (2014)} - Awarded for top overall performance within the company.
	{\bf IRI "Make It Happen" Award (2015)} - Awarded for completing a custom analysis for one of IRI's top clients under pressing timelines.
	
\end{resume}

\end{document}